---
title: "Feature Engineering"
date: "2025-08-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
library(jsonlite)
```
# Importing Raw Data
```{r}
burundi_crs <- readRDS("../data/Raw Data/bdi_result_crs.rds")
colombia_crs <- readRDS("../data/Raw Data/col_result_crs.rds")
```

```{r}
burundi_mptf <- readRDS("../data/Raw Data/bdi_result_mptf_nogovsig.rds")
colombia_mptf <- readRDS("../data/Raw Data/col_result_mptf_nogovsig.rds")
```

# Preprocessing
```{r}
dataframe <- c("crs", "mptf")
country_list <- c("burundi", "colombia")

for (DATASET in dataframe) {

for (COUNTRY in country_list) {
  
  COUNTRY_DATASET <- get(paste0(COUNTRY,"_", DATASET))

years <- names(COUNTRY_DATASET[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)

# subsetting country crs data by year
for (i in first_year:last_year) {
  COUNTRY_DATASET_i <- COUNTRY_DATASET[["edge_lists"]][[as.character(i)]]
  
  COUNTRY_DATASET_i <- COUNTRY_DATASET_i %>%
    mutate(Country = COUNTRY, Year = i, data = DATASET)
  
  assign(paste0(COUNTRY,"_", DATASET,"_", i), COUNTRY_DATASET_i)
}

# appending to make 1 per country per dataset
assign(
  paste0(COUNTRY, "_", DATASET, "_all_years"),
  bind_rows(mget(paste0(COUNTRY, "_", DATASET, "_", first_year:last_year)))
)

# cleaning the environment
rm(list = paste0(COUNTRY, "_", DATASET, "_", first_year:last_year), COUNTRY_DATASET_i, COUNTRY_DATASET)
rm(list = paste0(COUNTRY,"_",DATASET))
}
}
```

# binding to make one dataframe
```{r}
final_data <- NULL

for (COUNTRY in country_list) {
  for (DATASET in dataframe) {
    
    temp_data <- get(paste0(COUNTRY, "_", DATASET, "_all_years"))
    
    temp_data <- temp_data %>%
      map_df(as.character)
    
    final_data <- bind_rows(final_data, temp_data)
  }
}
```

# cleaning the environment
```{r}
rm(list = setdiff(ls(), "final_data"))
```

# filtering data to run test in JavaScript and saving
```{r}
test_data <- final_data %>%
  filter(Country == "burundi",
         data == "crs",
         Year == "2005")
```

# Need to export 2 data frames, a node and a edge data frame
- The node data frame needs a unique ID variable.
```{r}
test_data_nodes <- test_data %>%
  mutate(id = sender, orgtype = sender_orgtype) %>%
  select(id, orgtype) %>%
  bind_rows(
    test_data %>%
      mutate(id = receiver, orgtype = receiver_orgtype) %>%
      select(id, orgtype)
  ) %>%
  distinct(id, .keep_all = TRUE) %>%
  mutate(label = id) %>%
  select(id, label) # deselected orgtype for now
```

- the edge data frame needs:
id
source
target
type
```{r}
test_data_edges <- test_data %>%
  mutate(source = sender, target = receiver, id = 1:length(test_data$sender), type = "arrow") %>%
  select(id, source, target) # deselected type for now
```

# Checking if ID variables are unique
```{r}
any(duplicated(test_data_nodes$id))
any(duplicated(test_data_edges$id))
```

# Handling duplicated edges
Duplicate edges clusers the visual and gives a hairball appearance.
```{r}
any(duplicated(test_data_edges$source, test_data_edges$target))
```

```{r}
test_data_edges <- test_data_edges %>%
  group_by(source, target) %>%
  mutate(n_contracts = n()) %>%
  slice(1) %>%
  ungroup()
```

# Exporting data
```{r}
write_json(test_data, pretty = TRUE, path = "../data/Processed Data/test_data.json")
write_json(test_data_nodes, pretty = TRUE, path = "../data/Processed Data/test_data_nodes.json")
write_json(test_data_edges, pretty = TRUE, path = "../data/Processed Data/test_data_edges.json")
```

