---
title: "Feature Engineering"
date: "2025-08-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
library(jsonlite)
library(visNetwork)
library(openxlsx)
```
# Importing Raw Data
```{r}
burundi_crs <- readRDS("../data/Raw Data/bdi_result_crs.rds")
colombia_crs <- readRDS("../data/Raw Data/col_result_crs.rds")
```

```{r}
burundi_mptf <- readRDS("../data/Raw Data/bdi_result_mptf_nogovsig.rds")
colombia_mptf <- readRDS("../data/Raw Data/col_result_mptf_nogovsig.rds")
```

# Preprocessing
```{r}
dataframe <- c("crs", "mptf")
country_list <- c("burundi", "colombia")

for (DATASET in dataframe) {

for (COUNTRY in country_list) {
  
  COUNTRY_DATASET <- get(paste0(COUNTRY,"_", DATASET))

years <- names(COUNTRY_DATASET[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)

# subsetting country crs data by year
for (i in first_year:last_year) {
  COUNTRY_DATASET_i <- COUNTRY_DATASET[["edge_lists"]][[as.character(i)]]
  
  COUNTRY_DATASET_i <- COUNTRY_DATASET_i %>%
    mutate(Country = COUNTRY, Year = i, data = DATASET)
  
  assign(paste0(COUNTRY,"_", DATASET,"_", i), COUNTRY_DATASET_i)
}

# appending to make 1 per country per dataset
assign(
  paste0(COUNTRY, "_", DATASET, "_all_years"),
  bind_rows(mget(paste0(COUNTRY, "_", DATASET, "_", first_year:last_year)))
)

# cleaning the environment
rm(list = paste0(COUNTRY, "_", DATASET, "_", first_year:last_year), COUNTRY_DATASET_i, COUNTRY_DATASET)
rm(list = paste0(COUNTRY,"_",DATASET))
}
}
```

# binding to make one dataframe
```{r}
final_data <- NULL

for (COUNTRY in country_list) {
  for (DATASET in dataframe) {
    
    temp_data <- get(paste0(COUNTRY, "_", DATASET, "_all_years"))
    
    temp_data <- temp_data %>%
      map_df(as.character)
    
    final_data <- bind_rows(final_data, temp_data)
  }
}
```

# cleaning the environment
```{r}
rm(list = setdiff(ls(), "final_data"))
```

# filtering data to run test and saving
```{r}
test_data <- final_data %>%
  filter(Year %in% c("2007", "2008", "2016"))
```

# running test with data in visnetwork
```{r}
glimpse(test_data)
```
```{r}
test_data <- test_data %>%
  mutate(cost = as.numeric(cost),
         n_contracts = as.numeric(n_contracts),
         )

glimpse(test_data)
```


## Creating (test) Nodes Data

for the nodes dataframe i need:
- id = Sender and Receiver uniquely appended
- label = id
- group = organization types uniquely appended

```{r}
test_nodes <- test_data %>%
  mutate(id = sender, group = sender_orgtype) %>%
  select(id, group) %>%
  bind_rows(
    test_data %>%
      mutate(id = receiver, group = receiver_orgtype) %>%
      select(id, group)
  ) %>%
  distinct(id, .keep_all = TRUE) %>%
  mutate(label = id)
```

## Creating (test) Edges Data

For the edges, I will need:
- from = sender
- to = receiver
- value = (for now this will be the number of contracts. In the shiny app this will be customizeable between cost too)
- title = This can be a custom message. something saying "this is a contract from <sender> to <receiver>. the contract id is <id>. the number of contract between them is <n_contracts>. the sector is <sector>.

```{r}
test_edges <- test_data %>%
  mutate(from = sender, to = receiver) %>%
  select(from, to)
```

### edges weight variable
```{r}
test_edges1 <- test_edges %>%
  group_by(from, to) %>%
  mutate(value = n())%>%
  ungroup() %>%
  distinct(from, to, value, .keep_all = TRUE)
```

## Creating (test) Visual
```{r}
visNetwork(test_nodes, test_edges1) %>%
  visLayout(randomSeed = 123) %>%
  visEdges(arrows = "to") %>%
  visOptions(highlightNearest = TRUE)
```


# Exporting data
```{r}
saveRDS(test_data, "../data/Processed Data/test_data.rds")
```




















