---
title: "Feature Engineering"
date: "2025-08-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(purrr)
```
# Importing Raw Data
```{r}
burundi_crs <- readRDS("../data/Raw Data/bdi_result_crs.rds")
colombia_crs <- readRDS("../data/Raw Data/col_result_crs.rds")
```

```{r}
burundi_mptf <- readRDS("../data/Raw Data/bdi_result_mptf_nogovsig.rds")
colombia_mptf <- readRDS("../data/Raw Data/col_result_mptf_nogovsig.rds")
```

# Preprocessing
```{r}
country_list <- c("burundi", "colombia")

for (COUNTRY in country_list) {
  
  COUNTRY_crs <- get(paste0(COUNTRY, "_crs"))

years <- names(COUNTRY_crs[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)

# subsetting country crs data by year
for (i in first_year:last_year) {
  COUNTRY_crs_i <- COUNTRY_crs[["edge_lists"]][[as.character(i)]]
  
  COUNTRY_crs_i <- COUNTRY_crs_i %>%
    mutate(Country = COUNTRY, Year = i)
  
  assign(paste0(COUNTRY, "_crs_", i), COUNTRY_crs_i)
}

# appending to make 1 crs dataset per country
assign(
  paste0(COUNTRY, "_crs_all_years"),
  bind_rows(mget(paste0(COUNTRY, "_crs_", first_year:last_year)))
)

# cleaning the environment
rm(list = paste0(COUNTRY, "_crs_", first_year:last_year), COUNTRY_crs_i, COUNTRY_crs)
}
```

```{r}
years <- names(burundi_crs[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)

# subsetting country crs data by year
for (i in first_year:last_year) {
  burundi_crs_i <- burundi_crs[["edge_lists"]][[as.character(i)]]
  
  burundi_crs_i <- burundi_crs_i %>%
    mutate(Country = "Burundi", Year = i)
  
  assign(paste0("burundi_crs_", i), burundi_crs_i)
}

# appending to make 1 crs dataset per country
burundi_crs_all_years <- bind_rows(
  mget(paste0("burundi_crs_", first_year:last_year))
)

# cleaning the environment
rm(list = paste0("burundi_crs_", first_year:last_year), burundi_crs_i, burundi_crs)
```









# (Burundi) Extracting and Binding MPTF data by Country
years <- names(Burundi_MPTF[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)


for (i in first_year:last_year) {
  Burundi_MPTF_i <- Burundi_MPTF[["edge_lists"]][[as.character(i)]]
  
  Burundi_MPTF_i <- Burundi_MPTF_i %>%
    mutate(Country = "Burundi", Year = i)
  
  assign(paste0("Burundi_MPTF_", i), Burundi_MPTF_i)
}

Burundi_MPTF_all_years <- bind_rows(
  mget(paste0("Burundi_MPTF_", first_year:last_year))
)

rm(list = paste0("Burundi_MPTF_", first_year:last_year), Burundi_MPTF_i, Burundi_MPTF)

#-------

# (Colombia) Extracting and Binding CRS data by Country
years <- names(Colombia_CRS[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)

for (i in first_year:last_year) {
  Colombia_CRS_i <- Colombia_CRS[["edge_lists"]][[as.character(i)]]
  
  Colombia_CRS_i <- Colombia_CRS_i %>%
    mutate(Country = "Colombia", Year = i)
  
  assign(paste0("Colombia_CRS_", i), Colombia_CRS_i)
}

Colombia_CRS_all_years <- bind_rows(
  mget(paste0("Colombia_CRS_", first_year:last_year))
)

rm(list = paste0("Colombia_CRS_", first_year:last_year), Colombia_CRS_i, Colombia_CRS)

# (Colombia) Extracting and Binding MPTF data by Country
years <- names(Colombia_MPTF[["edge_lists"]]) %>% 
  as.numeric() %>% 
  sort()

first_year <- min(years)
last_year  <- max(years)


for (i in first_year:last_year) {
  Colombia_MPTF_i <- Colombia_MPTF[["edge_lists"]][[as.character(i)]]
  
  Colombia_MPTF_i <- Colombia_MPTF_i %>%
    mutate(Country = "Colombia", Year = i)
  
  assign(paste0("Colombia_MPTF_", i), Colombia_MPTF_i)
}

Colombia_MPTF_all_years <- bind_rows(
  mget(paste0("Colombia_MPTF_", first_year:last_year))
)

rm(list = paste0("Colombia_MPTF_", first_year:last_year), Colombia_MPTF_i, Colombia_MPTF)

}




